Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-08-30 Ben_Manuscripts/structure_paper/Draft.tex
intro rework

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqeuous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater, and organic micropollutants
  found in municipal and industrial wastewaters are a few examples of the
  diversity of components that make up various water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  one can reduce the number of required membrane passes and post-treatment steps,
  thus lowering the energy requirements of the separation processes.
  Additionally, one can extract valuable resources from the feed streams. For
  example, flowback water produced during hydraulic fracturing of shale
  formations contains dissolved species such as acetate whose extraction could be
  economically valuable.

@@

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions, however the porous architecture of
  commercially dominant membranes lack uniformity which severely impacts their
  selectivity. Although scalable, their fabrication involves the spontaneous
  assembly of polymers into disordered structures which offer separation pathways
  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
  Tortuosity increases the effective length that a solute must travel, while
  polydispersity limits membrane selectivity.

@@

  % (4) justify LLCs

  % (5) justify need for simulations

@@

@@

  Our current understanding of the molecular details of LLC membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. Over the past 20 years, H\textsubscript{II}-phase LLC
  polymer membrane studies have been limited primarily to Na-GA3C11 with some
  characterization done after minor structural modifications. Resel et al.~varied
  the length of the monomer tails and the counterion used and observed its effect
  on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
  performance, it was shown that membranes formed by cross- linked Na-GA3C11 in
  the H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
  diameter because the pores are too large \cite{zhou_supported_2005}. We do not
  yet understand how to controllably reduce the effective pore size or how to
  tune the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with
  molecular detail could provide sufficient information about the mechanisms and
  chemical features to better inform experimental design of similar
  nanostructured membranes.

>>>>

  More highly selective nanoporous membranes would be extremely useful in order
  to perform complex aqueous separations with seawater and various sources of
  wastewater. Sodium chloride and boron in seawater \cite{fritzmann_state---art_2007}, and organic micropollutants
  found in municipal and industrial wastewaters \cite{schwarzenbach_challenge_2006} are examples of the
  diverse constituents of various water sources. By efficiently
  separating contaminants from feed solutions with highly selective membranes,
  one can reduce the number of required membrane passes and post-treatment steps
  needed for a given filtration process \cite{werber_materials_2016}, thus lowering energy requirements.
  Additionally, one can extract valuable resources from the feed streams. For
  example, flowback water produced during hydraulic fracturing of shale
  formations contains dissolved species such as acetate whose extraction could be
  economically valuable \cite{dischinger_application_2017}.

@@

  Reverse osmosis (RO) and nanofiltration (NF) are two prevailing membrane
  filtration processes that can be used to separate solutes on the order of 1 nm
  in size and smaller, as well as ions, however the porous architecture of
  commercially dominant membranes lack uniformity which severely impacts their
  selectivity \cite{van_der_bruggen_review_2003}. Although scalable, their fabrication involves the spontaneous
  assembly of polymers into disordered structures which offer separation pathways
  that are tortuous and polydisperse in size \cite{werber_materials_2016}.
  Tortuosity increases the effective length that a solute must travel, while
  polydispersity limits membrane selectivity.

@@

@@

  % BJC14: (4) justify LLCs

@@

  % BJC14: (5) justify need for simulations
  % BJC14: dishchinger example seems like a good thing to bring up since they 
  % explicitly state in the paper that they need a better understanding of
  % transport
  Our current understanding of the molecular details of LLC membranes'
  nanostructure is not sufficient to be able to precisely design them for
  specific separations. Dischinger et al. attempted to use an empirical model
  that correlates the physiochemical properties of the counterion used in a 
  Q\textsubscript{I} phase LLC membrane to solute rejection\cite{dischinger_effect_2017}.
  Although their model showed some qualitative agreement with experiment, the
  quality of fit of their model was limited due to complex solute-membrane 
  interactions which could not easily be modeled. Additionally, they observed
  an unexpected discrepancy in the relationship between uncharged solute
  rejection and water permeability which will require a more in-depth knowledge of
  the difference between solute and solvent transport.

  Over the past 20 years, H\textsubscript{II}-phase LLC
  polymer membrane studies have been limited primarily to Na-GA3C11 with some
  characterization done after minor structural modifications. Resel et al.~varied
  the length of the monomer tails and the counterion used and observed its effect
  on pore spacing \cite{resel_structural_2000}.  In a later study of rejection
  performance, it was shown that membranes formed by cross-linked Na-GA3C11 in
  the H\textsubscript{II} phase cannot separate solutes less than 1.2 nm in
  diameter because the pores are too large \cite{zhou_supported_2005}. We do not
  yet understand how to controllably reduce the effective pore size or how to
  tune the chemical environment in the nanopores of this or related materials for
  small molecule separations. The only source of predictive modeling for LLC
  systems have been macroscopic models that likely do not adequately describe
  transport at these length scales \cite{hatakeyama_water_2011}. Modeling with
  molecular detail could provide sufficient information about the mechanisms and
  chemical features to better inform experimental design of similar
  nanostructured membranes.
